Optimising Heterogeneous Ambulance Fleet Allocations in Jakarta

### 2024-08-12 tex/main.tex
add comments from Paul

Exact synchronicity considerations are shown in Figure~\ref{fig:sequential_logic}:
\begin{itemize}
  \item whenever the secondary vehicle reaches the patient before the primary
  has left, vehicle, they remain with the patient until the primary vehicle
  leaves;
  \item if secondary vehicle arrives after the primary vehicle has left, they
  will immediately return to their stations as they are not needed at the scene;
  \item if the expected time for the secondary vehicle to reach the patient
  exceeds the expected time for the primary vehicle to reach the patient then
  the secondary vehicle is not deployed, and so that transit job would be
  abandoned in the secondary simulation (although still seen by a primary
  vehicle in the initial simulation). We assume that secondary vehicles must
  still reach the pickup locations, due to potential difficulties in
  communication en-route. \textcolor{red}{Consider a situation when a
  secondary vehicle arrives and the patient does not require a hospital, with
  better en-route communication this would mean the primary vehicle turns
  around, however without en-route communication which is assumed here, the
  primary vehicle must still reach the patient pick-up location.}
\end{itemize}

@@

\section*{Acknowledgements}
We would like to express our sincere gratitude to Indonesian emergency ambulance
providers including 118 and 119 for their support, insights and provision of
data. In particular we wish to thank Professor Aryono Djuned Pusponegoro and Ms
Asti Puspita Rini, Founder and Director of 118 Ambulance Service Foundation and
Dr Winarto, Head of the 119 Ambulance Service in Jakarta.

>>>>

Exact synchronicity considerations are shown in Figure~\ref{fig:sequential_logic}:
\begin{itemize}
  \item whenever the secondary vehicle reaches the patient before the primary
  has left, vehicle, they remain with the patient until the primary vehicle
  leaves;
  \item if secondary vehicle arrives after the primary vehicle has left, they
  will immediately return to their stations as they are not needed at the scene;
  \item if the expected time for the secondary vehicle to reach the patient
  exceeds the expected time for the primary vehicle to reach the patient then
  the secondary vehicle is not deployed, and so that transit job would be
  abandoned in the secondary simulation (although still seen by a primary
  vehicle in the initial simulation). We assume that secondary vehicles must
  still reach the pickup locations, due to potential difficulties in
  communication en-route. \textcolor{red}{Consider a situation when a
  secondary vehicle arrives and the patient does not require transportation to
  a hospital, with better en-route communication this would mean the primary
  vehicle turns around, however without en-route communication which is
  assumed here, the primary vehicle must still reach the patient pick-up
  location.}
\end{itemize}

@@

\section*{Acknowledgements}
We would like to express our sincere gratitude to Indonesian emergency ambulance
providers including 118 and 119 for their support, insights and provision of
data. In particular we wish to thank Professor Aryono Djuned Pusponegoro and Ms
Asti Puspita Rini, Founder and Director of 118 Ambulance Service Foundation and
Dr Winarto, Executive Director of the 119 Ambulance Service (now PK3D) in Jakarta.
